cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Updated the equations

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
```

@@

```{r, label = "fig-quadratic-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` data."}
#| fig-width: 15
#| fig-height: 5

quadratic_proj1 + quadratic_proj2 + quadratic_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-cubic-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cubic` data."}
#| fig-width: 15
#| fig-height: 5

cubic_proj1 + cubic_proj2 + cubic_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-scurve-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` data."}
#| fig-width: 15
#| fig-height: 5

scurve_proj1 + scurve_proj2 + scurve_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

```{r, label = "fig-scurvehole-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurvehole` data."}
#| fig-width: 15
#| fig-height: 5

scurvehole_proj1 + scurvehole_proj2 + scurvehole_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

>>>>

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm'),
     plot.margin = margin(0, 0, 0, 0)
   )
)
```

@@

@@

```{r, label = "fig-cubic-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` and `cubic` data."}
#| fig-width: 15
#| fig-height: 10

quadratic_proj1 + quadratic_proj2 + quadratic_proj3 +
cubic_proj1 + cubic_proj2 + cubic_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

@@

@@

```{r, label = "fig-scurve-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` and `scurvehole` data."}
#| fig-width: 15
#| fig-height: 10

scurve_proj1 + scurve_proj2 + scurve_proj3 + 
  scurvehole_proj1 + scurvehole_proj2 + scurvehole_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

### 2025-06-24 paper-cardinalR.tex
Updated the equations

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-quadratic-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `quadratic` data.}\label{fig:fig-quadratic-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubic-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `cubic` data.}\label{fig:fig-cubic-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-scurve-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurve` data.}\label{fig:fig-scurve-proj}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-scurvehole-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurvehole` data.}\label{fig:fig-scurvehole-proj}
\end{figure}

>>>>

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubic-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `quadratic` and `cubic` data.}\label{fig:fig-cubic-proj}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-scurve-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurve` and `scurvehole` data.}\label{fig:fig-scurve-proj}
\end{figure}
